% My resume based on Jake's Resume template

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\setlength{\footskip}{4.08003pt}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
 \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Hanz Nathan Po} \\ \vspace{1pt}
    \small (647)-674-2006 $|$ \href{mailto:hanznathanpo@gmail.com}{\underline{hanznathanpo@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/hanznathanpo/}{\underline{linkedin.com/in/hanznathanpo}} $|$
    \href{https://github.com/HanzPo}{\underline{github.com/HanzPo}} $|$
    \href{https://www.hanzpo.com/}{\underline{hanzpo.com}}
\end{center}


%-----------Projects-----------
\section{Projects}
\resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Albumify - Automated Album Covers for Spotify Playlists - Hack the North Project} \\ \emph{React.js, JavaScript, CSS, Chakra UI, FastAPI, Python}}{Sept. 2023}
          \resumeItemListStart
            \resumeItem{Developed the user interface and frontend logic for Albumify, a web application aimed at automatic album cover generation for Spotify playlists, using React, JavaScript, and Chakra UI.}
            \resumeItem{Collaborated effectively with a multidisciplinary team of four to bring Albumify from concept to reality, using tools such as Git and GitHub.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
 \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Skills Canada Coding Competition - 1st in Ontario} \\ \emph{Java, Maven}}{May. 2023}
          \resumeItemListStart
            \resumeItem{Competed against representatives from 19 school boards across Ontario to create CRUD program in one day}
            \resumeItem{Utilized Java to read and write to a database containing recipe information, display recipes in an accessible format, filter recipes based on dietary restrictions, and calculate ingredients based on provided servings.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
    
     \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{STEM Fellowship Big Data Challenge} \\ \emph{Python, Matplotlib, Pandas, Scikit-learn}}{Nov. 2021 -- Feb. 2022}
          \resumeItemListStart
            \resumeItem{Analyzed the correlation between economic factors such as GDP, Human Development Index scores (HDI) against how much of a country's energy comes from emission-free and renewable sources}
            \resumeItem{Utilized Pandas to import and parse large datasets, observed patterns using Scikit-learn's regression functions, then visualized interesting findings through Matplotlib \& Geopandas (world maps, scatter plots, line graphs)}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EXTRACURRICULARS-----------
\section{Extracurriculars}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Computer Science Club - Co-founder and President}}{May. 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Led and organized regular club meetings, fostering a collaborative learning environment with workshops on various computer science-related topics including web development, tools such as Git, and contest preparation.}
            \resumeItem{Promoted enrichment opportunities such as hackathons and competitions in order to encourage hands-on experiences among members.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Model United Nations Club - President}}{Sep. 2022 -- Present}
          \resumeItemListStart
            \resumeItem{Facilitated training of all club members in preparation for conferences}
            \resumeItem{Organized school delegations to several conferences for the first time in club history}
            \resumeItem{Secured club funding, making conferences accessible to more students}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
    
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Student Intern - Leadership Department}{Oct. 2022 -- Jun. 2023}
      {Toronto Catholic District School Board $|$ \emph{Co-op}}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Design promotional material for board-wide events, including posters, videos, and animations with tools such as Canva, Illustrator, and Premiere Pro}
        \resumeItem{Analyze data regarding student involvement and participation in 31 high schools across Toronto}
      \resumeItemListEnd
    \resumeSubHeadingListEnd




%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Francis Libermann Catholic High School}{Toronto, ON}
      {Ontario Secondary School Diploma (OSSD) $|$ Expected Graduation Jun. 2024}{Sep. 2020 -- Present}
      \resumeItemListStart
        \resumeItem{STEM Program - One of 52 students selected from 250+ applicants}
        \resumeItem{Honour Roll (2021, 2022, 2023)}
        \resumeItem{Finalist at school science fair, bronze medal at Toronto Science Fair}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------


%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Soft Skills}{: Communication, collaboration, leadership, problem solving, interpersonal, analytical skills} \\
     \textbf{Languages}{: English (Native), Hokkien, Mandarin, Tagalog, French} \\
     \textbf{Programming Languages}{: C++, JavaScript, Python, C\# (for Unity engine), Java, HTML, CSS} \\
     \textbf{Tools}{: Git, Github, Visual Studio Code, Eclipse, Jupyter Notebook, Unity 3D, Vite, Node.js} \\
     \textbf{Libraries}{: React, Express, Pandas, NumPy, Matplotlib, Scikit-learn, Tkinter}
    }}
 \end{itemize}
%-------------------------------------------
\end{document}
